---
title: "Flagged Sample Report"
author: "WQ-Review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
        html_document:
                toc: true
                toc_depth: 3
                fig_width: 15
                fig_height: 9
                css: style.css
                
---
```{r setup, include=FALSE}
###Load libraries and setup options

require(WQReview)
require(plyr)
require(knitr)
opts_chunk$set(dev = 'png',out.width='1024px',out.height='750px',dpi=60)
```

```{r,echo=FALSE}
###Pull data
qw.data <- suppressWarnings(readNWISodbc(DSN=DSN,
                                 env.db = env.db,
                                 qa.db=qa.db,
                                 STAIDS=STAIDS,
                                 begin.date=begin.date,
                                 end.date=end.date)
)
                             
###Run report generation on qw.data 
reports <- NULL

        ######################################
        #######Run report generation##########
        ######################################
        
        tryCatch({
                ###Run ion balance function
                ionBalanceOut <- suppressWarnings(ionBalance(qw.data = qw.data,wide=TRUE))
                chargebalance.table <- ionBalanceOut$chargebalance.table
                reports$BalanceDataTable <- ionBalanceOut$BalanceDataTable
                reports$balanceTable <- ionBalanceOut$chargebalance.table
                
                ###Check that a balance was calculated
                if(nrow(chargebalance.table) > 0)
                {
                        
                        ###Join charge balance table to plot table
                        chargebalance.table <- chargebalance.table[c("RECORD_NO","sum_cat","sum_an","perc.diff","complete.chem")]
                        qw.data$PlotTable <- join(qw.data$PlotTable,chargebalance.table[!duplicated(chargebalance.table$RECORD_NO), ],by="RECORD_NO")
                        
                        
                } else {}
                
        }, warning = function(w) {
                ###Run ion balance function
                ionBalanceOut <- ionBalance(qw.data = qw.data,wide=TRUE)
                chargebalance.table <- ionBalanceOut$chargebalance.table
                reports$BalanceDataTable <- ionBalanceOut$BalanceDataTable
                reports$balanceTable <- ionBalanceOut$chargebalance.table
                
                ###Check that a balance was calculated
                if(nrow(chargebalance.table) > 0)
                {
                        
                        ###Join charge balance table to plot table
                        chargebalance.table <- chargebalance.table[c("RECORD_NO","sum_cat","sum_an","perc.diff","complete.chem")]
                        qw.data$PlotTable <- join(qw.data$PlotTable,chargebalance.table[!duplicated(chargebalance.table$RECORD_NO), ],by="RECORD_NO")
                        
                        
                } else {}
                warning(w,"This caused a warning DO NOT REPORT UNLESS YOU NOTICE A PROBLEM WITH PERFORMANCE")
        }, error = function(e) {
                errors <- print("Error with charge balance. please report this on the github issues page")
                        
        })
        
        tryCatch({
                
                ###Run repTabler
                reports$repTable <- suppressWarnings(repTabler(qw.data))
        
        }, warning = function(w) {
                
                ###Run repTabler
                reports$repTable <- repTabler(qw.data)
                warning(w,"This caused a warning DO NOT REPORT UNLESS YOU NOTICE A PROBLEM WITH PERFORMANCE")
        }, error = function(e) {
                errors <- print("Error with replicate table. please report this on the github issues page")
        })
        

        tryCatch({
                ###Run wholevPart
                reports$wholevpartTable <- suppressWarnings(wholevPart(qw.data))
                
        }, warning = function(w) {
                ###Run wholevPart
                reports$wholevpartTable <- wholevPart(qw.data)
                warning(w,"This caused a warning DO NOT REPORT UNLESS YOU NOTICE A PROBLEM WITH PERFORMANCE")
        }, error = function(e) {
                errors <- print("Error with whole vs part table. please report this on the github issues page")
                
        })
        

        ###Generate chem flag summary
        tryCatch({
                reports$chemFlagTable <- suppressWarnings(chemCheck(qw.data))
        },
        warning = function(w) {
                reports$chemFlagTable <- suppressWarnings(chemCheck(qw.data))
        },
        error = function(e) {
                errors <- print("Error with auto sample flagging, please report this on the github issues page")
        })
        
        ###Generate chem flag summary
        tryCatch({
                reports$pestFlagTable <- suppressWarnings(pestCheck(qw.data))
        },
        warning = function(w) {
                reports$pestFlagTable <- suppressWarnings(pestCheck(qw.data))
        },
        error = function(e) {
                errors <- print("Error with auto sample flagging, please report this on the github issues page")
        })
        
        ###Generate sample flag summary
        tryCatch({
                reports$sampleFlagTable <- suppressWarnings(flagSummary(qw.data))
                ###Need to reset row names
                rownames(reports$sampleFlagTable) <- seq(from = 1, to = nrow(reports$sampleFlagTable))
                },
                warning = function(w) {
                        reports$sampleFlagTable <- suppressWarnings(flagSummary(qw.data))
                        ###Need to reset row names
                        rownames(reports$sampleFlagTable) <- seq(from = 1, to = nrow(reports$sampleFlagTable))
                        
                        },
                error = function(e) {
                        errors <- print("Error with auto sample flagging, please report this on the github issues page")
                        })
        
        ###Generate result flags
        tryCatch({
                reports$resultFlagTable <- suppressWarnings(historicCheck(qw.data,returnAll=FALSE))
                ###Need to reset row names
                rownames(reports$resultFlagTable) <- seq(from = 1, to = nrow(reports$resultFlagTable))
                },
                warning = function(w) {
                
                        reports$resultFlagTable <- suppressWarnings(historicCheck(qw.data,returnAll=FALSE)) 
                        ###Need to reset row names
                        rownames(reports$resultFlagTable) <- seq(from = 1, to = nrow(reports$resultFlagTable))
                        },
                error = function(e) {
                        print("Error with auto result flagging, please report this on the github issues page")
                })
        
```
        

#Flagged tables
##Sample-level flags
```{r,echo=FALSE}
require(DT)
############################
###sampleFlagTable
############################


###Render the table
#datatable(
        reports$sampleFlagTable,
        extensions = list(FixedColumns = list(leftColumns = 5)),
        options = list(
                scrollX=TRUE,
                autoWidth=TRUE)
)
```

##Result-level flags

```{r,echo=FALSE}
require(DT)

############################
###resultFlagTable
############################

###Render the table

datatable(
        reports$resultFlagTable,
        extensions = list(FixedColumns = list(leftColumns = 5)),
        options = list(
                scrollX=TRUE,
                autoWidth=TRUE)
)

#kable(reports$resultFlagTable)

```

```{r, echo=FALSE, results='asis',message=FALSE,warning=FALSE}
require(gridExtra)
sites <- unique(na.omit(reports$sampleFlagTable[c("SITE_NO","STATION_NM")]))
for(i in 1:nrow(sites))
{
        cat("#",sites$STATION_NM[i],"\n")
        
        ###Run charge balance checks
        if(all(!is.na(reports$sampleFlagTable$BadCB_30.21[which(reports$sampleFlagTable$SITE_NO == sites$SITE_NO[i])])))
        {
        cat("## Chargbalance flag plots","\n")
        cbPlot <- qwcbPlot(qw.data,
                           site.selection = sites$SITE_NO[i],
                           highlightrecords = unique(reports$sampleFlagTable$RECORD_NO),
                           print=FALSE)
        scSumPlot <- qwscSumPlot(qw.data,
                           site.selection = sites$SITE_NO[i],
                           highlightrecords = unique(reports$sampleFlagTable$RECORD_NO),
                           print=FALSE)
        grid.arrange(cbPlot,scSumPlot,nrow=1,ncol=2)
        cat("\n\n")

        }else{}
        
        ###Run result checks
        cat("## Result flag plots","\n")
        resultFlags <- subset(reports$resultFlagTable,SITE_NO == sites$SITE_NO[i])
        parms <- unique(resultFlags[c("PARM_CD","PARM_NM","PARM_SEQ_GRP_CD")])
        parms <- subset(parms, PARM_SEQ_GRP_CD %in% c("INN","INM","NUT","SED") | PARM_CD %in% c("00095","00061","00400","00010"))
        
        for(k in 1:nrow(parms))
                {
                
                cat("###",parms$PARM_CD[k],parms$PARM_NM[k],"\n")
                
                tsPlot <- qwtsPlot(qw.data = qw.data,
                   site.selection = sites$SITE_NO[i],
                   plotparm = parms$PARM_CD[k],
                   highlightrecords = unique(reports$resultFlagTable$RECORD_NO[which(reports$resultFlagTable$PARM_CD == parms$PARM_CD[k])]),
                   print = FALSE)
                
                seasonalPlot <- qwseasonalPlot(qw.data,
                               site.selection = sites$SITE_NO[i],
                               plotparm = parms$PARM_CD[k],
                               highlightrecords = unique(reports$resultFlagTable$RECORD_NO[which(reports$resultFlagTable$PARM_CD == parms$PARM_CD[k])]),
                               print = FALSE)
                
                pqPlot <- qwparmParmPlot(qw.data,
                         site.selection = sites$SITE_NO[i],
                         yparm = parms$PARM_CD[k],
                         xparm = "00061",
                         highlightrecords = unique(reports$resultFlagTable$RECORD_NO[which(reports$resultFlagTable$PARM_CD == parms$PARM_CD[k])]),
                         print = FALSE)
                
                pSCPlot <- qwparmParmPlot(qw.data,
                          site.selection = sites$SITE_NO[i],
                          yparm = parms$PARM_CD[k],
                          xparm = "00095",
                          highlightrecords = unique(reports$resultFlagTable$RECORD_NO[which(reports$resultFlagTable$PARM_CD == parms$PARM_CD[k])]),
                          print = FALSE)
                
                grid.arrange(tsPlot,seasonalPlot,pqPlot,pSCPlot,nrow=2,ncol=2)
                cat("\n\n")
        }

                



        
}


