---
title: "`r paste(network,' Network Summary',sep='')`"
author: "WQ-Review"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---
```{r setup, include=FALSE}
###Load libraries and setup options

require(WQReview)
require(plyr)
require(knitr)
opts_chunk$set(dev = 'png',out.width='1024px',out.height='750px',dpi=60)
```

```{r,echo=FALSE}
###Load up the data
load(paste(outputDir,"/data.rda",sep=""))
###Subset to site network
qw.data$PlotTable <- subset(qw.data$PlotTable,SITE_NO %in% sites)
reports$chemFlagTable <- subset(reports$chemFlagTable, SITE_NO %in% sites)
reports$pestFlagTable <- subset(reports$pestFlagTable, SITE_NO %in% sites)   
reports$resultFlagTable <- subset(reports$resultFlagTable, SITE_NO %in% sites)  

```

#Network Data Summary
* ###Most recent data modification: `r format(max(qw.data$PlotTable$RESULT_MD),"%Y-%m-%d %H:%M","\n")`

+ Site:`r unique(qw.data$PlotTable$STATION_NM[which(qw.data$PlotTable$RESULT_MD == max(qw.data$PlotTable$RESULT_MD))])`

+ Parameters modified:`r qw.data$PlotTable$PARM_CD[which(qw.data$PlotTable$RESULT_MD == max(qw.data$PlotTable$RESULT_MD))]`

+ Who:`r qw.data$PlotTable$RESULT_MN[which(qw.data$PlotTable$RESULT_MD == max(qw.data$PlotTable$RESULT_MD))]`

* ###Total Samples waiting for review:
+ Records with DQI of **I**:`r length(unique(qw.data$PlotTable$RECORD_NO[which(qw.data$PlotTable$DQI_CD == "I")]))`

+ Records with DQI of **S**:`r length(unique(qw.data$PlotTable$RECORD_NO[which(qw.data$PlotTable$DQI_CD == "S")]))`


+ Total number of records:`r length(unique(qw.data$PlotTable$RECORD_NO))`

#Flagged tables
##Basic chemical flags
```{r,echo=FALSE}
require(DT)
############################
###chemFlagTable
############################


###Render the table
datatable(
        reports$chemFlagTable,
        extensions = list(FixedColumns = list(leftColumns = 5)),
        options = list(
                scrollX=TRUE,
                autoWidth=TRUE)
)
#kable(reports$chemFalgTable)
```

##Pesticide flags
```{r,echo=FALSE}
require(DT)
############################
###pestFlagTable
############################


###Render the table
datatable(
        reports$pestFlagTable,
        extensions = list(FixedColumns = list(leftColumns = 5)),
        options = list(
                scrollX=TRUE,
                autoWidth=TRUE)
)
```

##Result flags

```{r,echo=FALSE}
require(DT)

############################
###resultFlagTable
############################

###Render the table

datatable(
        reports$resultFlagTable,
        extensions = list(FixedColumns = list(leftColumns = 5)),
        options = list(
                scrollX=TRUE,
                autoWidth=TRUE)
)

#kable(reports$resultFlagTable)

```


```{r, echo=FALSE, results='asis',message=FALSE,warning=FALSE}
###Make links for each site
cat("\n\n")
for(l in 1:length(sites))
    {
    cat("#[",
        unique(qw.data$PlotTable$SITE_NO[which(qw.data$PlotTable$SITE_NO == sites[l])]),
        " ",
        unique(qw.data$PlotTable$STATION_NM[which(qw.data$PlotTable$SITE_NO == sites[l])]),
        "](",
        unique(qw.data$PlotTable$SITE_NO[which(qw.data$PlotTable$SITE_NO == sites[l])]),
        ".htm)",
        "\n",
        sep=""
    )
        
}
```
